\racets: Faceted Execution in Racket

### 2018-07-24 paper/paper.tex
added c-m cite

Similarly, program counters are sets of branches. However, we must
still ask how we will keep track of the ``current'' program
counter. Our implementation uses Racket's parameters, though other
mechanisms (such as continuation marks\kris{cite}, to which parameters
macro-expand) can also be used. \racets defines the parameter
\code{current-pc}, and updates it as computation progresses:

>>>>

Similarly, program counters are sets of branches. However, we must
still ask how we will keep track of the ``current'' program
counter. Our implementation uses Racket's parameters, though other
mechanisms (such as continuation marks~\cite{clements2001modeling}, to which parameters
macro-expand) can also be used. \racets defines the parameter
\code{current-pc}, and updates it as computation progresses:
